Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-01 GWLDCII.tex
some more typos and minor wording changes

The next several lemmas assume $V$ and $W$ to be as above. They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$. In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure \ref{fig Le} and Lemma \ref{lem shape}). This last row contains three (new) plusses. All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$. (See Lemmas \ref{lem n and n-1} to Theorem \ref{thm dim}.

We proceed to address the cases laid out in \ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_n^W= I_n^V \cup {n-3}$.

@@

Now suppose $c = v= n-4$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$.  Thus $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.

@@

Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

  \end{itemize}
The first three points follow immediately from Lemmas \ref{lem n and n-1} through \ref{lem other k}. If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for. If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for: namely those in positions $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.

>>>>

The next several lemmas assume $V$ and $W$ to be as above. They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$. In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure~\ref{fig Le} and Lemma~\ref{lem shape}). This last row contains three (new) plusses. All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemmas~\ref{lem n and n-1} to Theorem~\ref{thm dim}.

We proceed to address the cases laid out in Lemma~\ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_1^W= I_1^V \cup \{n-3\}$.

@@

Now suppose $c = v= n-4$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$, namely the plusses in positions $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.

@@

Thus $W$ has one of the two configurations depicted in Figure~\ref{fig special p}, and by Remark~\ref{rem n-2 case} we can further assume that if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

  \end{itemize}
The first two points follow from Lemmas \ref{lem n and n-1} through \ref{lem n-2 bad}. The third point follows from Lemma~\ref{lem other k}, which tells us that the $n-3$ column of $V$ is identical to the $n-2$ column of $W$ (excluding the last row).

Finally, if $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for. On the other hand, if $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$. This plus is paired with the one plus in $W$ yet unaccounted for, namely the one in position $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.
